---
title: "Maple Syrup Here We GO!!!"
author: "Guadalupe Chimil, Annah Lee, Ivette Viramontes"
date: "4/11/2018"
output: 
  html_document:
    df_print: paged   
    code_folding: hide 
---  
Sap from maple trees is collected and boiled down to produce maple syrup. Collection occurs in the early spring, during “sugaring season”. In order for the sap to run, temperatures must be above freezing during the day and below freezing at night. As spring temperatures in New England are notoriously variable, so too is the sugaring yield. Climate change also affects the beginning of spring. Use the maple_sap data on gallons of sap collected and the weather data to predict the start date, end date, and yield for sugaring season. Since you only have a few years worth of data on temperature and sap, you may need to consult external data to deepen your analysis.

<<<<<<< HEAD
```{r}   
#devtools::install_github("beanumber/macleish",version="0.3.3")  
#packageVersion("macleish")
 
library(tidyverse)  
=======
```{r} 
# devtools::install_github("beanumber/macleish")
#library(macleish)
#packageVersion("macleish") 

library(tidyverse)
>>>>>>> f1de6879f0019317a2601dfd2be1c28590b75b50
library(macleish)
library(leaflet)  
library(devtools)  
library(sf) 
<<<<<<< HEAD
library(ggplot) 
library(dplyr)  
library(stringr) 
=======
library(leaflet)
```
>>>>>>> f1de6879f0019317a2601dfd2be1c28590b75b50

```

```{r} 
<<<<<<< HEAD
View(maple_sap)

=======
library(tidyverse)
library(leaflet)
library(devtools)
library(macleish)
library(sf)
library(ggplot2)
library(dplyr)
#Renaming Forests
>>>>>>> f1de6879f0019317a2601dfd2be1c28590b75b50
forests <- macleish_layers[["forests"]] %>%
  rename(forest_type = Sheet1__Na) 
View(forests) 

mapleforests <- forests %>% 
filter(forest_type == "Sugar Maple Forest")
View(mapleforests)

maple_map <- leaflet() %>% 
  addTiles() %>% 
  addPolylines(data = macleish_layers[["boundary"]], weight = 1)
maple_map %>%  
  addPolylines(data = mapleforests)%>% 
  addPolylines(data = mapleforests, weight = 1, color = "red")    

View(whately_2015)    

forests <- macleish_layers[["forests"]] %>%   
  rename(forest_type = Sheet1__Na)

#Maple Forests Data
mapleforests <- forests %>%
filter(forest_type == "Sugar Maple Forest")

#Maple Forests Map
maple_map <- leaflet() %>%
  addTiles() %>%
  # Boundaries
  addPolygons(data = macleish_layers[["boundary"]], weight = 1, fillOpacity = 0.01, group = "Boundaries") %>%
  addPolylines(data = macleish_layers[["boundary"]], weight = 1) %>%
  addPolylines(data = mapleforests, weight = 3, color = "	#FF0000") %>%
  addPolylines(data = macleish_layers[["trails"]], weight = 2, color = "#8B4513") %>%
  addPolylines(data = macleish_layers[["streams"]], weight = 2 , color = "#191970") %>% 
  addLegend("bottomright",  
  colors =c("#8B4513",  "#191970", "#FF0000"),
  labels= c("trails", "streams", "Maple Forest"),
  title= "Macleish Legend",
  opacity = 0.7)
maple_map 

#mac <- etl("macleish") %>%
  #etl_update()
#whately <- mac %>%
  #tbl("whately") %>%
  #collect(n = Inf)

# Filtering Weather Data
whately <- whately[-c(1),] %>%
  mutate(year = substr(when, 0, 4)) %>%
  mutate(date = substr(when, 0, 10)) %>%
  mutate(time = substr(when, 12, 16)) %>%
  filter(year %in% c("2013","2014","2015","2017")) %>%
  filter(time %in% c("00:00","12:00"))

#Renaming Maple Sap Data
maple_sap <- rename(maple_sap, date = when) %>%
    mutate(year = substr(date, 0, 4))

#Filtering and Joining Weather and Maple Sap Data
syrup_data <- merge( x= maple_sap, y= whately, by = c("date", "year"), all= TRUE) 
syrup_data <- syrup_data %>% filter(!is.na(sap)) 

<<<<<<< HEAD
syrup_plot <- ggplot(syrup_data,aes(x=year,y=weather))+
  geom_point() 

syrup_plot +
  geom_point(aes(size=sap))+
  labs(title="Sap collected per year")

``` 
=======

#Syrup Data by Year
syrup_data2013 <- syrup_data %>% filter(year == "2013" & time == "12:00")
syrup_data2014 <- syrup_data %>% filter(year == "2014" & time == "12:00")
syrup_data2015 <- syrup_data %>% filter(year == "2015" & time == "12:00")
syrup_data2017 <- syrup_data %>% filter(year == "2017" & time == "12:00")

#Graphs
syrup_plot <- ggplot(data= syrup_data2013, aes(x= data, y=as.numeric(temperature))) + geom_point(size = "sap")
syrup_plot





```
>>>>>>> f1de6879f0019317a2601dfd2be1c28590b75b50
